---
title: "Lab 03"
author: "Aicha Sidiya"
date: "9 May 2023"
editor_options: 
  chunk_output_type: console
output:
  pdf_document: default
---

# Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(sf)
``` 

# Data

```{r load-data, message = FALSE}
fl_votes <- st_read("data/fl_votes.shp", quiet = TRUE)
fl_votes %>%
  slice(1:6)
```


# Exercise 1

```{r add-winner}
fl_votes <- fl_votes %>% 
  mutate(winner20 = if_else(rep20 > dem20, TRUE, FALSE))
```


# Exercise 2

```{r fl-plot-1}
ggplot(fl_votes) +
  geom_sf(aes(fill = winner20)) +
  scale_fill_manual(values = c("#0015BC", "#DE0100" )) +
  labs(title = "Florida’s 2020 U.S. Presidential election results",
       fill = "winner") + 
  theme_bw() 


```

# Exercise #3

```{r fl-props}
fl_votes <- fl_votes %>% 
  mutate(prop_rep16 = rep16/(rep16 + dem16),
         prop_rep20 = rep20/(rep20 + dem20))
```

# Exercise 4

```{r fl-plot-2}
ggplot(fl_votes) +
  geom_sf(aes(fill = prop_rep20),) +
  scale_fill_gradient(low = "#DE0100", high = "#0015BC") +
  labs(title = "Florida’s 2020 U.S. Presidential election results",
       fill = "Republican Vote Share") + 
  theme_bw() 

```

# Exercise 5

```{r fl-change}
fl_votes <- fl_votes %>% 
  mutate(diff_rep = prop_rep20 - prop_rep16)
```

# Exercise 6

```{r fl-plot-3}
ggplot(fl_votes) +
  geom_sf(aes(fill = diff_rep)) +
  scale_fill_gradient2(low = "#DE0100", 
                       mid = "white", 
                       high = "#0015BC", 
                       midpoint = 0) +
  labs(title = "Change in Republican Vote Share (2016-2020)",
       fill = "Vote Share Difference") + 
  theme_bw() 
```

# Exercise 7

7.	What do the visualizations you developed tell you about the 2016 and 2020 Presidential election in Florida? What are limitations of these visualizations?

The northern country of florida have a higher number of republicans, as per the second map. The central counties votes were very close to each other the republican share was close to 50%. Nonetheless, these county still had their vote shores decrease from 2016 to 2020 based on the third map. Some counties of the south had a significant increase of their vote shares of republican. The first visualisation wasn't representative beacuse it only stated who one in each county without presenting the proportion of the win.  

